% !TEX program = xelatex

\documentclass{resume}

\begin{document}

\name{Andrii Semko}

\basicInfo{
  \email{semko.andrey.i@gmail.com} \textperiodcentered\ 
  \phone{+380631697060} \textperiodcentered\ 
  \linkedin[andriisem]{https://www.linkedin.com/in/andriisem} \textperiodcentered\ 
  \github[andriisem]{https://github.com/andriisem}}

\section{Summary}
Senior Software Engineer with 9+ years building B2B SaaS products. Led microservices and cloud infrastructure (GCP, Terraform, Kubernetes) on a full-stack stack (Python, TypeScript, Vue.js) for a platform serving thousands of businesses; owned reliability, delivery, and client-facing technical leadership end to end.

\section{Experience}

\datedsubsection{\textbf{WiseStamp}, Kyiv, Ukraine (Remote)}{Feb. 2019 -- Present}
\role{Senior Software Engineer}{}

\homepage[wisestamp.com]{https://www.wisestamp.com/}
\begin{itemize}
  \item \textbf{Technical Leadership:} Led architecture and delivery of greenfield microservices (Python, Node.js, TypeScript), owning system design, Vue.js/Tailwind UI implementation, and production rollout across a multi-service B2B SaaS platform.
  \item \textbf{Platform \& Infrastructure:} Managed GCP infrastructure with Terraform, Kubernetes, and Docker; built scalable backend services with Redis and Elasticsearch, improving deployment reliability and reducing operational toil.
  \item \textbf{Revenue \& Reliability:} Owned reliability and performance of core production services (Redis, Elasticsearch, CI/CD), reducing downtime and incident-driven churn while supporting subscription growth and enterprise retention.
  \item \textbf{Team \& Delivery:} Drove sprint planning and backlog prioritization aligned with product goals; mentored engineers through code reviews and technical standards, raising team throughput and reducing rework.
  \item \textbf{Client \& Business Impact:} Acted as technical lead in client-facing engagements, translating business needs into shippable solutions and supporting account growth, renewals, and upsell opportunities.
\end{itemize}

\datedsubsection{\textbf{BITEGRICO}, Kyiv, Ukraine}{Oct. 2018 -- Sep. 2019}
\role{Lead Software Engineer}{}

\homepage[bitegri.co]{https://www.bitegri.co/}
\begin{itemize}
  \item \textbf{Product Delivery:} Led development of ERP/CRM services (Python, PostgreSQL) that automated sales and operations workflows, reducing manual work and increasing client throughput per engagement.
  \item \textbf{Engineering Leadership:} Served as lead engineer---set technical direction, introduced Docker-based DevOps on AWS/GCP, and owned delivery of business-critical modules tied directly to client revenue.
  \item \textbf{Team Building:} Owned hiring end to end, recruiting and onboarding engineers to expand delivery capacity for new client projects.
\end{itemize}

\datedsubsection{\textbf{ERP Ukraine}, Kyiv, Ukraine}{Jan. 2017 -- Oct. 2018}
\role{Software Engineer}{}

\homepage[erp.co.ua]{http://erp.co.ua/}
\begin{itemize}
  \item Built core ERP/CRM services and Ukrainian accounting localization (Python, PostgreSQL), enabling compliant reporting and tax workflows that strengthened the product's domestic market offering.
\end{itemize}

\datedsubsection{\textbf{MPS Development}, Kyiv, Ukraine}{Jan. 2016 -- Dec. 2017}
\role{Software Engineer}{}

\homepage[mpsdevelopment.net]{http://mpsdevelopment.net/}
\begin{itemize}
  \item Engineered large-scale price-monitoring pipelines (Python, Selenium) with automated test coverage, delivering competitive market data that supported client pricing and margin decisions.
\end{itemize}

\section{Education}
\datedsubsection{\textbf{National Technical University of Ukraine
"Igor Sikorsky Kyiv Polytechnic Institute"}, Ukraine, Kyiv} {2017 - 2018}
\textit{Master's degree} in Materials science and Computer Simulation

\datedsubsection{\textbf{National Technical University of Ukraine
"Igor Sikorsky Kyiv Polytechnic Institute"}, Ukraine, Kyiv} {2013 - 2017}
\textit{Bachelor degree} in Engineering materials science 

\section{Skills}
\begin{itemize}[parsep=0.5ex]
    \item Languages: Python, JavaScript, TypeScript, Node.js
    \item Backend \& APIs: Flask, REST, Microservices, System Design, Technical Leadership
    \item Data \& Messaging: PostgreSQL, MongoDB, Redis, Elasticsearch, GCP Datastore, Kafka
    \item Cloud \& DevOps: GCP, AWS, Azure, Terraform, Kubernetes, Docker, CI/CD, Git
    \item Frontend: Vue.js, Tailwind CSS
\end{itemize}

\section{Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Blog: \homepage[andriisem.github.io]{https://andriisem.github.io/}
  \item Languages: English (professional working proficiency), Ukrainian (native)
\end{itemize}

\end{document}
